Reviewer(s)' Comments to Author

### 2019-01-03 papers/lang2018/referee_comments.tex
Added section on speedup

This is timely and a really nice piece of work. This Cis-interface has the potential to become a major tool to support the future development of the plant systems model integration. I have a few specific comments on this and would like the author to address. 
\begin{todolist}
\item First, it would be great to have a more clear description of the novelty of the pipeline developed. Is it mainly a compilation of existing tools, in that case, this needs to be clearly indicated. If not, then a clear statement in this might be great. 
\item[\done] Secondly, the work will benefit a lot from a more explicit description of a user case. For example, clearly write out the exact commands needed to finish one round of code integration. 
\item Thirdly, I would be keen to show some performance data of integration of different modules. No data are provided on this at this stage. 
\item Fourthly, the main purpose of this paper is to describe a platform which can help plant modelers of different research areas and using programming languages work together more effectively and easily, it would be great if author can explain the advantage of this new software from the perspective of users. 
\item Fifthly,  many of the software engineering methodologies described in the paper are widely used in the field of software engineering. It would be better to provide some more concrete description of how this particular tool help users.  
\item Finally, it would be helpful to provide a flow chart and pseudo-code of the core algorithms used to link different modules.
\end{todolist}

@@

We would like to thank the reviewer for their comments as we believe they helped make the paper much stronger and to better represent the work being described. We will address the reviewer's comments in the order they were raised:
\begin{enumerate}
\item ?
\item We whole heartedly agree with the reviewer that the manuscript greatly benefits from a concrete use case. As such, we have added a new section ``Worked Example" after the methods section that walks through, step-by-step, integration of the example models presented in the introduction. The code from the example is available on the paper branch of the {\pkg} GitHub repository and will be published as part of the documentation during the 1.0 release.
\item We believe that the reviewer is referring to performance data on integration of specific biological \emph{models}, but would appreciate some clarification if this is not the case. While we would like to show concrete example of the performance of some integrations done with {\pkg}, many of the integration are still in the pre-publication stage. As the code for the models is not yet public, these performance tests would not be informative to those without access. In addition, the performance increase to parallelism is highly dependent on how coupled the two models are. If two model are integrated as in the case of the added root/shoot integration example as they are, the shoot model will always be waiting for the root model to complete its calculation and there not be a speedup over scripted integration of the two models via an intermediary file. However, the shoot model had other calculations to perform before it needed the data from the root model, a speedup would be possible and completely dependent on the ratio of independent calculations to dependent calculations and the time required for model communication. The speedup calculation is even more complex when more than two models are involved. To reflect this complex relationship, we have added a subsection to the end results section entitled ``Speedup" that discusses this and present a equation for calculating the speedup for an integration of two models given the appropriate parameters.
\item ?
\item ?
\item ?
\end{enumerate}

>>>>

This is timely and a really nice piece of work. This Cis-interface has the potential to become a major tool to support the future development of the plant systems model integration. I have a few specific comments on this and would like the author to address. 
\begin{todolist}
\item First, it would be great to have a more clear description of the novelty of the pipeline developed. Is it mainly a compilation of existing tools, in that case, this needs to be clearly indicated. If not, then a clear statement in this might be great. 
\item[\done] Secondly, the work will benefit a lot from a more explicit description of a user case. For example, clearly write out the exact commands needed to finish one round of code integration. 
\item[\done] Thirdly, I would be keen to show some performance data of integration of different modules. No data are provided on this at this stage. 
\item Fourthly, the main purpose of this paper is to describe a platform which can help plant modelers of different research areas and using programming languages work together more effectively and easily, it would be great if author can explain the advantage of this new software from the perspective of users. 
\item Fifthly,  many of the software engineering methodologies described in the paper are widely used in the field of software engineering. It would be better to provide some more concrete description of how this particular tool help users.  
\item Finally, it would be helpful to provide a flow chart and pseudo-code of the core algorithms used to link different modules.
\end{todolist}

@@

We would like to thank the reviewer for their comments as we believe they helped make the paper much stronger and to better represent the work being described. We will address the reviewer's comments in the order they were raised:
\begin{enumerate}
\item ?
\item We whole heartedly agree with the reviewer that the manuscript greatly benefits from a concrete use case. As such, we have added a new section ``Worked Example" after the methods section that walks through, step-by-step, integration of the example models presented in the introduction. The code from the example is available on the paper branch of the {\pkg} GitHub repository and will be published as part of the documentation during the 1.0 release.
\item We believe that the reviewer is referring to performance data on integration of specific biological \emph{models}, but would appreciate some clarification if this is not the case. While we would like to show concrete examples of the performance of some integrations done with {\pkg} using actual models, most of the models that {\pkg} has been used with are still in the pre-publication stage. As the code for the models is not yet public, these performance tests would not be informative to those without access. In addition, the performance increase due to parallelism is highly dependent on how coupled the models are and how many models are part of the integration. If two models are integrated that are tightly coupled, one model will always be waiting for the other to complete its calculation and there not be a speedup over scripted integration of the two models via an intermediary file. However, if one model had other calculations to perform before it needed the data from the other model, a speedup would be possible and completely dependent on the ratio of independent calculations to dependent calculations and the time required for model communication. The speedup calculation is even more complex when more than two models are involved. To reflect this complex relationship, we have added a subsection to the end of the results section entitled ``Speedup from Parallels" that discusses this and present an equation for calculating the speedup for an integration of two models given the appropriate parameters.
\item ?
\item ?
\item ?
\end{enumerate}
